Coalescent inference of mutation spectrum histories from sample frequency spectra

### 2019-08-27 manuscript/main.tex
fig tweak

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/model}
\caption{Schematic of the marked Poisson process model with $n=4$.
We condition on coalescent times $T_4=t_4,T_3=t_3,T_2=t_2$ and consider mutation intensity function $\mu(t)$.
Red dots indicate mutation events placed by time $t$, genomic position $x$, and coalescent line (which are depicted as extruded in the genomic coordinate axis, grey rectangles).
The probability that a differential element $dxdt$ on a given sheet contains a mutation is proportional to the instantaneous mutation intensity $\mu(t)$.
}
\label{fig:model}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/model}
\caption{Schematic of the marked Poisson process model with $n=4$.
We condition on coalescent times $T_4=t_4,T_3=t_3,T_2=t_2$ and consider mutation intensity function $\mu(t)$.
Red dots indicate mutation events placed by time $t$, genomic position $x$, and coalescent line (which are depicted as extruded in the genomic coordinate axis, grey sheets).
The probability that a differential element $dxdt$ on a given sheet contains a mutation is proportional to the instantaneous mutation intensity $\mu(t)$.
}
\label{fig:model}
\end{figure}
